A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-07-12 paper/project.tex

\subsection{Water confined to a slit}

@@

\subsubsection{Two rods - hydrophobic interaction}

>>>>

We compute the density profile and surface tension by relaxing a slab
of water in a periodic unit cell.  This slab has two surfaces, so the
surface tension is just half the free energy of the cell, divided by
its cross-sectional area.  As mentioned in
section~\ref{sec:empirical}, the $b$ parameter is determined by
setting this surface tension to match the experimental value.  The
associated density profile is plotted in
Figure~\ref{fig:cartesianDensity}, which displays two peaks in
density.

@@

\subsubsection{Two rods - interaction effects}
